---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
.dynamic-comment {background-color: #FFEEFF;
  padding: 12px;
  border-radius: 8px;}
```

# Tracking Instagram Ads in My Feed

```{r}
library(tidyverse)
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTAPHXsVQfubHC3wws5HW69hadD5WhRB23Igz7jG6yNAjk4KAX9Pg8frUER8GmZRaQ7Q4nNM8wYPPMU/pub?gid=1004960971&single=true&output=csv"

logged_data <- read_csv(csv_file)

latest_data <- logged_data %>%
  rename(timestamp = 1, 
         rate_of_interest = 2, 
         ad_category = 3, 
         ad_format = 4,
         brand_repeat = 5,
         interaction = 6) %>%
  mutate(rate_of_interest = as.numeric(rate_of_interest), 
         brand_repeat = as.numeric(brand_repeat))
```
## Summary Values:

```{r}
average_interest <- mean(latest_data$rate_of_interest, na.rm = TRUE)
max_brand_repeat <- max(latest_data$brand_repeat, na.rm = TRUE)
yes_interaction <- latest_data %>%
  filter(interaction == "Yes") %>%
  nrow()
```

::: dynamic-comment
So far, `r nrow(latest_data)` ads have been logged in this dataset.
`r yes_interaction` of these ads involved interaction from the viewer.

The average interest rating was `r round(average_interest, 1)` out of 5.
The highest number of times the same brand appeared in one day was `r max_brand_repeat`.
:::

The chart below shows the number of ads in each category. 

```{r}
ggplot(latest_data, aes(x = ad_category)) +
  geom_bar(fill = "#FFC0CB") +
  labs(title = "Number of Ads by Category",
    x = "Ad category",
    y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
```{r}
top_category <- latest_data %>%
  count(ad_category, sort = TRUE) %>%
  slice(1) %>%
  pull(ad_category)

top_category_count <- latest_data %>%
  count(ad_category, sort = TRUE) %>%
  slice(1) %>%
  pull(n)

```
::: dynamic-comment
The most common ad category in this dataset was **`r top_category`**, with `r top_category_count` ads recorded.
:::

The chart shows whether viewers interacted with the ads they saw.

```{r}
ggplot(latest_data, aes(x = interaction)) +
  geom_bar(fill = "#89CFF0") +
  labs(title = "Number of Ads by Interaction",
    x = "Interaction with ad",
    y = "Count") +
  theme_minimal()

```
```{r}
yes_interaction <- latest_data %>%
  filter(interaction == "Yes") %>%
  nrow()

no_interaction <- latest_data %>%
  filter(interaction == "No") %>%
  nrow()
```
::: dynamic-comment
Out of all logged ads, `r yes_interaction` involved interaction, while `r no_interaction` did not.
:::
